A Case Study in Preserving a High Energy Physics Application

### 2014-03-14 paper.tex
adjust the sequence of table 1

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        Ntuples data    & HDFS& 11.6TB & 43.3GB & 20GB \\ \hline
        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        HOME dir& AFS &10.2GB & N/A & 32MB\\ \hline
        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \begin{tablenotes}
      \small
      \item The first column illustrates the total size of each data and software source; 
            the second column illustrates the size of the named files from each source;
            the third column illustrates the size of acutally used data from each source.
            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
    \end{tablenotes}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

\begin{table*}
    \centering
    \begin{tabular}{|l|r|r|r|}
        \hline
        \bf Solution ID & \bf Data Resources &\bf Software Resources & \bf Operation Manual \\ \hline
        Solution 1& Grid & CMSSW Git HTTP & email \\ \hline
        Solution 2 and 3& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
        Solution 4& package & package & user manual of package \\ \hline
    \end{tabular}
    \caption{Relationship of Different Solutions}
    \label{table:relationship}
\end{table*}

@@

%*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software. if changed, one new package is generated to avoid data overlap and pollution. otherwise, directly starts packaging process based on the current target package. 
\section{Evaluation}
The section first illustrates the relationship of different preservation and reproduction solutions, then the platform used to evaluate different solutions is introduced. The execution time and data size of Solution 2 and 4 are tested and compared. It is hard to accurately calculate the time consumption of Solution 1. Solution 3 shares the same time consumption and data size with Solution 3.

\subsection{Relationship of Different Solutions}
The relationship of these four solutions to repeat one program is shown in Table~\ref{table:relationship}. Each new solution tries to make it easier to repeat one program through making the data and software preparation easier.

@@

This solution does not support mining of implicit dependencies.
The size of data and software from each category is shown in table~\ref{table:datasize-2nd}, which only lists the size of each clear dependency.

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    \bf Data Category & \bf Data Size \\ \hline
    Software from CMSSW & 448.3MB \\ \hline
    Software from Git & 73.7MB \\ \hline
    Software from Wget & 52MB \\ \hline
    HDFS & 43.3GB \\ \hline
    Total & 43.86GB \\ \hline
    \end{tabular}
    \caption{Data Size of Solution 2}
    \label{table:datasize-2nd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|r|}
    \hline
    \bf Data &\bf Location & \bf Data \\ 
    \bf Category & & \bf Size\\ \hline
    HDFS & hadoop &20GB \\ \hline
    PanFS & pscratch & 1.6MB \\ \hline
    CVMFS & cvmfs &103MB \\ \hline 
    NFS & opt &53KB \\ \hline
    AFS & afs &34MB \\ \hline
    Local FS& bin etc lib lib64 sbin tmp usr&68.3MB \\ \hline
    Total & &21GB \\ \hline
    \end{tabular}
    \caption{Data Size of Solution 4}
    \label{table:datasize-3rd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Data Category & \bf Solution2: Size & \bf Solution4: Size \\ \hline
    HDFS & 43.3GB & 20GB \\ \hline
    PanFS & 155TB & 1.6MB \\ \hline
    CVMFS & 7.4GB &103MB \\ \hline
    NFS & 862GB &53KB \\ \hline
    AFS & 10.2GB &34MB \\ \hline
    Local FS& 110GB&68.3MB \\ \hline
    Total & 156TB &21GB \\ \hline
    \end{tabular}
    \caption{Data Size Comparison beweeen Solution 2 and 4}
    \label{table:datasize-2nd3rd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Task & \bf Solution 2& \bf Solution 4\\ 
    \bf Category & \bf Time & \bf Time \\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 3s \\ \hline
    Obtain file namelist & N/A & 28min 23s \\ \hline
    Generate package & N/A & 85min 51s \\ \hline
    Actual Analysis & 20min 31s & 13min 4s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 4}
    \label{table:time-2nd3rd}
\end{table}

>>>>

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
        Ntuples data    & HDFS& 11.6TB & 43.3GB & 20GB \\ \hline
        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
        HOME dir& AFS &10.2GB & N/A & 32MB\\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \begin{tablenotes}
      \small
      \item The first column illustrates the total size of each data and software source; 
            the second column illustrates the size of the named files from each source;
            the third column illustrates the size of acutally used data from each source.
            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
    \end{tablenotes}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

@@

%*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software. if changed, one new package is generated to avoid data overlap and pollution. otherwise, directly starts packaging process based on the current target package. 
\section{Evaluation}
The section first introduces the platform used to evaluate different solutions is introduced. The execution time and data size of Solution 2 and 4 are tested and compared. It is hard to accurately calculate the time consumption of Solution 1. Solution 3 shares the same time consumption and data size with Solution 3.

@@

This solution does not support mining of implicit dependencies.

@@

@@

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Task & \bf Solution 2& \bf Solution 4\\ 
    \bf Category & \bf Time & \bf Time \\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 3s \\ \hline
    Actual Analysis & 20min 31s & 13min 4s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 4}
    \label{table:time-2nd3rd}
\end{table}
